Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-21 paper.tex
save

To form flat clusters out of the hierarchy, one must decide on a maximum
distance threshold above which clusters are considered to correspond to
distinct authors.  Exploiting knowledge from the partial clusters known in
$\bar{{\cal C}}$, we evaluate the following semi-supervised cut-off strategies:
\begin{itemize}
\item \textit{No cut:} all signatures from the same block are assumed to be from the same author.
\item \textit{Global cut:} the threshold is chosen globally over all blocks,
    as the one maximizing some score $f(\bar{{\cal C}}, \widehat{\bar{{\cal C}}}_t)$.
\item \textit{Block cut:} the threshold is chosen locally at each block $b$,
    as the one maximizing some score $f(\bar{{\cal C}}^b, \widehat{\bar{{\cal C}}^b_t})$.
    In case $\bar{{\cal C}}^b$ is empty, then all signatures from $b$ are clustered together.
\end{itemize}
Where $\widehat{\bar{{\cal C}}}_t$ denotes the predicted clusters, restricted to the
signatures in $\bar{{\cal C}}$, when cutting the hierarchy at threshold $t$, and
where $\bar{{\cal C}^b}$ is limited to signatures of $\bar{{\cal C}}$ in block $b$.

\glnote{Notations should be improved and be made more explicit}

>>>>

To form flat clusters out of the hierarchy, one must decide on a maximum
distance threshold above which clusters are considered to correspond to
distinct authors. Let us denote by $\bar{{\cal S}} = \{ s | s \in \bar{c}, \bar{c}
\in \bar{\cal C} \}$ the set of all signatures for which partial clusters are
known. Let us also denote by $\widehat{\cal C} = \{ \widehat{c}_i | i = 0, ...,
K-1 \}$ the predicted clusters for all signatures in ${\cal S}$, and by
$\widehat{\overline{\cal C}} = \{ \widehat{c}_i \cap \bar{{\cal S}} | i = 0,
..., K-1 \}$ the predicted clusters restricted to signatures for which partial
clusters are known. From these, we evaluate the following semi-supervised cut-off strategies:
\begin{itemize}
\item \textit{No cut:} all signatures from the same block are assumed to be from the same author.
\item \textit{Global cut:} the threshold is chosen globally over all blocks,
    as the one maximizing some score $f(\bar{\cal C}, \widehat{\overline{\cal C}})$.
\item \textit{Block cut:} the threshold is chosen locally at each block $b$,
    as the one maximizing some score $f(\bar{\cal C}_b, \widehat{\overline{\cal C}}_b)$.
    In case $\bar{\cal C}_b$ is empty, then all signatures from $b$ are clustered together.
\end{itemize}

\glnote{Add a figure showing the three possible splits}
